---
title: ravindra-raut_resume
author: ravindra-raut
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles_html.css', 'resume']
    # css: ['css/custom_resume.css', 'css/styles_pdf.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
params:
  doctype: "HTML" # "PDF" or "HTML" is automatically updated in update_resume.R 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

#load packages
library(glue)

#source helper functions
source('helper_functions.R')


# get data from xlsx file
# position_data <- readxl::read_excel('resume_data.xlsx',
#                                     sheet = "positions",
#                                     na = c("", "NA", "na"))
# 
# skill_data <- readxl::read_excel('resume_data.xlsx',
#                                  sheet = "skills",
#                                  na = c("", "NA", "na"))

position_data <- read.csv('./data/position_data.csv', stringsAsFactors = F)
skill_data <- read.csv('./data/skill_data.csv', stringsAsFactors = F)
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r contactinfo}

# Adjust contact info based on document type - html has link while pdf does not
if(params$doctype == "HTML") {
  glue::glue('
    - <i class="fas fa-home"></i> Nanded, Maharashtra, India
    - <i class='fa fa-phone'></i> (+91) 700 190 2565
    - <i class='fa fa-envelope'></i> [raviraut206@gmail.com](raviraut206@gmail.com)
    - <i class='fa fa-github'></i> [github.com/Ravindra-Raut](https://github.com/Ravindra-Raut/)
    - <i class='fa fa-linkedin'></i> [ravindra-raut](https://www.linkedin.com/in/ravindra-raut-9402bb69/)
    - <i class='fa fa-laptop'></i> [ravindra-raut.netlify.app](https://ravindra-raut.netlify.app/)
  ')
} 

if(params$doctype == "PDF") {
  glue::glue('
    - <i class="fas fa-home"></i> Nanded, Maharashtra, India
    - <i class='fa fa-phone'></i> (+91) 700 190 2565
    - <i class='fa fa-envelope'></i> [raviraut206@gmail.com](raviraut206@gmail.com)
    - <i class='fa fa-github'></i> [github.com/Ravindra-Raut](https://github.com/Ravindra-Raut/)
    - <i class='fa fa-linkedin'></i> [ravindra-raut](https://www.linkedin.com/in/ravindra-raut-9402bb69/)
    - <i class='fa fa-laptop'></i> [ravindra-raut.netlify.app](https://ravindra-raut.netlify.app/)
  ')
}

```



```{r download}
# if doctype is html add link to download a pdf version
if(params$doctype == "HTML"){
  cat("[<i class='fas fa-download'></i> Download as a PDF](https://github.com/mleary/resume/raw/main/mleary_resume.pdf)")
}

```

<br>


Tech skills {#skills}
--------------------------------------------------------------------------------

```{r codingskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "Tech")

```

R skills {#rpackages}
--------------------------------------------------------------------------------

```{r rskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "R Packages")

```

Learning Focus {#interests}
--------------------------------------------------------------------------------

```{r learningfocus, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "Interests")

```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------


```{r}

# set disclaimer in bottom right corner based on doctype
if(params$doctype == "HTML") {
  glue::glue("
    Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
    Source code: [**Github repo**](https://github.com/mleary/resume).
  ")
} 
if(params$doctype == "PDF") {
  glue::glue("
    Made w/ **pagedown::html_resume**
    Code: **github.com/mleary/resume** 
  ")
}
```


Last updated on `r Sys.Date()`.
<br>
<br>


Main
================================================================================


Ravindra Raut {#title}
--------------------------------------------------------------------------------
I am currently investigating the impact of transposable elements on the adaptation of the rice genome under fungal pathogen challenges and genome duplication. Experienced in using next-generation sequencing technologies like shotgun sequencing, linked reads, and long-read sequencing for whole-genome resequencing, variant calling, transcriptome assembly, differential expression analysis, and developing pipelines. Interested in working on next-generation approaches, solving complex problems relating to genomic plasticity and epigenetics.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}
print_section(position_data, 'education')
```



Research Experience {data-icon=flask}
--------------------------------------------------------------------------------

```{r jobs}
print_section(position_data, 'research_positions')
```

